\section{Anti-uniqueness effects in Russian \label{sec:anti-uniqueness-russian}}
Anti-uniqueness effects are possible in both predicative and argumental definites in Russian, when DP-internal \textit{only} (pronounced as \textit{edinstvennyj} in Russian) is in the scope of negation, just as in English. While there is clear evidence of argumental anti-uniqueness, Russian speakers have mixed judgments on sentences with \textit{edinstvennyj} in the object position. In the idiolects of some speakers, anti-uniqueness effects do not arise in sentences whose English counterparts do have them. Additionally, argumental anti-uniqueness effects are possible even with verbs of non-creation in Russian.

\subsection{Predicative anti-uniqueness in Russian}
Definite descriptions can be predicative in Russian, as (\ref{pred-def}) and (\ref{pred-def2}) show.

\begin{exe}
	\ex \label{pred-def} \gll Dmitrij --- vysokij, simpati\v{c}nyj, i samyj umnyj student vo vs\"{e}m universitete.\\
	Dmitri {} tall cute and most smart student in all university\\
	\glt `Dmitri is tall, cute and the smartest student in the whole university.'
	
	\ex[*] { \label{pred-def2}  \gll Dmitrij --- vysokij, simpati\v{c}nyj, i Boris.\\
	Dmitri {} tall cute and Boris\\
	\glt `Dmitri is tall, cute and Boris.'
	}
\end{exe}

Assuming that (a) adjectives are of type $\langle e, t \rangle$ and proper names are of type $e$ in Russian, and (b) conjuncts must have the same semantic type, then the ability of a definite description in (\ref{pred-def}) to conjoin with an adjective, and the inability of a proper name to do so in (\ref{pred-def2}), indicates that definites can have type $\langle e, t \rangle$. The equivalent sentences without conjunction are grammatical (see (\ref{dmitri-boris}) and (\ref{dmitri-boris2}), so it is crucially the adjectival conjunction that renders the sentence with \textit{Boris} ungrammatical.\footnote{That is, the sentence is ungrammatical on an equative reading where \textit{Boris} has type $e$. It does have a grammatical reading where \textit{Boris} is taken to denote a set of properties associated with ``Boris-ness'', similarly to \textit{such-a} phrases in English: \begin{exe} \ex He's such a Boris.\end{exe} Russian speakers may find the reading more accessible with a name like \textit{Putin} that is more easily given a property reading. Since this property-denoting interpretation of \textit{Boris} plausibly has type $\langle e, t \rangle$, its grammaticality supports my assertion.} Note that the superlative \textit{samyj umnyj student} `smartest student' was used to force the determinate interpretation, since superlatives are inherently determinate but regular bare nominals can be either determinate or indeterminate.

\begin{exe}
	\ex \label{dmitri-boris} \gll Dmitrij --- samyj umnyj student vo vs\"{e}m universitete.\\
	Dmitri {} most smart student in all university\\
	\glt `Dmitri is the smartest student in the whole university.'
	
	\ex \label{dmitri-boris2} \gll Dmitrij --- Boris.\\
	Dmitri {} Boris\\
	\glt `Dmitri is Boris.'
\end{exe}

It has therefore been established that definite descriptions can be predicates in Russian. Do Russian predicative definites exhibit anti-uniqueness effects? (\ref{tolstoy}) and (\ref{tolstoy2}) indicate that they do.

\begin{exe}
	\ex \label{tolstoy} \gll Tolstoj --- edinstvennyj avtor \textit{Vojny i mira}.\\
	Tolstoy {} only author \textit{War and Peace}\\
	\glt `Tolstoy is the only author of \textit{War and Peace}.'
	
	\ex \label{tolstoy2} \gll Tolstoj ne edinstvennyj avtor \textit{Vojny i mira}.\\
	Tolstoy not only author \textit{War and Peace}\\
	\glt `Tolstoy is not the only author of \textit{War and Peace}.'
\end{exe}

(\ref{tolstoy2}) has the same meaning as its English translation. It presupposes that Tolstoy is an author of \textit{War and Peace} (since (\ref{tolstoy}) still entails that he is an author of \textit{War and Peace}) and asserts that one or more others are also authors. Therefore, \textit{edinstvennyj avtor Vojny i mira} `the only author of \textit{War and Peace}' fails to refer to an individual, just as in English, and must be an anti-unique definite.

\subsection{Argumental anti-uniqueness in Russian}
The basic pattern of argumental anti-uniqueness in English holds in Russian as well: nominals in the scope of negation modified by \textit{edinstvennyj} cannot be interpreted as determinate.

The basic paradigm is established by (\ref{anna1})-(\ref{anna3}). The second sentence in each numbered example, separated for clarity, should be read as a continuation of the first. (\ref{anna1}) and (\ref{anna2}) both entail a single lecture, so \textit{edinstvennuju lekciju} `the only lecture' is determinate and the pronoun \textit{ona} `it' in the continuation sentence can refer to it.

(\ref{anna3}) entails multiple lectures, so \textit{edinstvennuju lekciju} should be indeterminate and, as predicted, the pronoun in the continuation sentence cannot refer to it.

\begin{exe}
	\ex \label{anna1} \begin{xlist}
		\ex \gll Anna posetila edinstvennuju lekciju, kotoruju pro\v{c}ital Xomskij, kogda byl v na\v{s}em universitete.\\
		Anna attended only lecture which gave Chomsky when was at our university\\
		\glt `Anna went to the only lecture that Chomsky gave at our university.'
		
		\ex \gll Ona byla o lingvistike.\\
		it was about linguistics\\
		\glt `It was about linguistics.'
	\end{xlist}
	
	\ex \label{anna2} \begin{xlist}
		\ex \gll Anna ne posetila edinstvennuju lekciju, kotoruju pro\v{c}ital Xomskij, kogda byl v na\v{s}em universitete.\\
		Anna not attended only lecture which gave Chomsky when was at our university\\
		\glt `Anna didn't go to the only lecture that Chomsky gave at our university.'
		
		\ex \gll Ona byla o lingvistike.\\
		it was about linguistics\\
		\glt `It was about linguistics.'
	\end{xlist}
	
	\ex \label{anna3} \begin{xlist} 
		\ex \gll Anna posetila ne edinstvennuju lekciju, kotoruju pro\v{c}ital Xomskij, kogda byl v na\v{s}em universitete.\\
		Anna attended not only lecture which gave Chomsky when was at our university\\
		\glt `Anna went to one of the lectures that Chomsky gave at our university.'
		
		\ex \gll \# Ona byla o lingvistike.\\
		{} it was about linguistics\\
		\glt `It was about linguistics.'
	\end{xlist}
\end{exe}

Note that Russian uses two different sentences to express the same two readings as sentences that are ambiguous in English, like (\ref{only-goal}) (though see below for an exception).

The Russian data is more complicated than the tidy contrast in (\ref{anna1})-(\ref{anna3}) would suggest, however. For one thing, some speakers \textit{do} permit the continuation in (\ref{anna3}). This phenomenon will be addressed in section \ref{sec:no-anti-unique}. For another, some speakers find (\ref{anna2}) marginal and prefer to state it as in (\ref{anna2.1}). In examples to follow, I will use the variants corresponding to (\ref{anna2}) and not (\ref{anna2.1}) for consistency, as all speakers agreed that one or the other was grammatical.

\begin{exe}
	\ex \label{anna2.1} \gll Ne Anna posetila edinstvennuju lekciju, kotoruju pro\v{c}ital Xomskij, kogda byl v na\v{s}em universitete.\\
	Not Anna attended only lecture which gave Chomsky when was at our university\\
	\glt `It wasn't Anna that went to the only lecture that Chomsky gave at our university.'
\end{exe}

Some speakers interpret (\ref{anna3}) as entailing that Anna attended more than one of Chomsky's lectures, while others interpret it to mean that she attended only one (but that Chomsky gave more than one).

The word \textit{edinstvennyj} requires greater context in Russian than DP-internal \textit{only} does in English. Most speakers judge (\ref{bad-edinstvennyj}) to be bad, for example. For that reason, the \textit{edinstvennyj} phrases throughout this section bear relative clauses or prepositional phrases to give the necessary context for their use to be grammatical in Russian.

\begin{exe}
	\ex[*] { \label{bad-edinstvennyj} \gll Anna zabil edinstvennyj gol.\\
	Anna scored only gol.\\
	\glt Intended: `Anna scored the only goal.'
	}
\end{exe}

Despite these caveats, the generalization remains that argumental anti-uniqueness occurs in Russian where \citeauthor{cb2015} predict it would. This generalization is borne out across a range of different verbs and sentences:

\begin{exe}
	\ex \begin{xlist}
		\ex \gll Marija napisala edinstvennuoe xoro\v{s}oe so\v{c}inenie vo vs\"{e}m klasse.\\
		Maria wrote only good essay in entire class\\
		\glt `Maria wrote the only good essay in the entire class.'
		
		\ex \gll Ono bylo o russkoj literature.\\
		it was about Russian literature\\
		\glt `It was about Russian literature.'
	\end{xlist}
		
	\ex \begin{xlist}
		\ex \gll Marija ne napisala edinstvennuoe xoro\v{s}oe so\v{c}inenie vo vs\"{e}m klasse.\\
		Maria not wrote only good essay in entire class\\
		\glt `Maria didn't write the only good essay in the entire class.'
		
		\ex \gll Ono bylo o russkoj literature.\\
		it was about Russian literature\\
		\glt `It was about Russian literature.'
	\end{xlist}

	\ex \label{maria3} \begin{xlist}
		\ex \gll Marija napisala ne edinstvennuoe xoro\v{s}oe so\v{c}inenie vo vs\"{e}m klasse.\\
		Maria wrote not only good essay in entire class\\
		\glt `Maria wrote one of the good essays in the class.'
	
		\ex \gll \# Ono bylo o russkoj literature.\\
		{} it was about Russian literature\\
		\glt `It was about Russian literature.'
	\end{xlist}

	\ex \begin{xlist}
		\ex \gll Boris proizn\"{e}s edinstvennuju xoro\v{s}uju re\v{c}' na svad'be.\\
		Boris gave only good speech at wedding\\
		\glt `Boris gave the only good speech at the wedding.'
		
		\ex \gll Ono bylo o molodo\v{z}\"{e}nax.\\
		it was about newlyweds\\
		\glt `It was about the newlyweds.'
	\end{xlist}

	\ex \begin{xlist}
		\ex \gll Boris ne proizn\"{e}s edinstvennuju xoro\v{s}uju re\v{c}' na svad'be.\\
		Boris not gave only good speech at wedding\\
		\glt `Boris didn't give the only good speech at the wedding.'
		
		\ex \gll Ono bylo o molodo\v{z}\"{e}nax.\\
		it was about newlyweds\\
		\glt `It was about the newlyweds.'
	\end{xlist}
	
	\ex \label{boris3} \begin{xlist}
		\ex \gll Boris proizn\"{e}s ne edinstvennuju xoro\v{s}uju re\v{c}' na svad'be.\\
		Boris gave not only good speech at wedding\\
		\glt `Boris gave one of the good speeches at the wedding.'
		
		\ex \gll \# Ono bylo o molodo\v{z}\"{e}nax.\\
		{} it was about newlyweds\\
		\glt `It was about the newlyweds.'
	\end{xlist}
\end{exe}

Interestingly, Russian also evinces anti-uniqueness effects with verbs of non-creation like \textit{uvidet'} `to see' and \textit{probovat'} `to taste':

\begin{exe}
	\ex \begin{xlist}
		\ex \gll Lena uvidela edinstvennogo krokodila, kotoryj byl v zooparke.\\
		Lena saw only crocodile which was at zoo\\
		\glt `Lena saw the only crocodile at the zoo.'
		
		\ex \gll On byl dlinoy tri metra.\\
		it was lengthwise three meters\\
		\glt `It was three meters long.'
	\end{xlist}

	\ex \begin{xlist}
		\ex \gll Lena ne uvidela edinstvennogo krokodila, kotoryj byl v zooparke.\\
		Lena not saw only crocodile which was at zoo\\
		\glt `Lena didn't see the only crocodile at the zoo.'
		
		\ex \gll On byl dlinoy tri metra.\\
		it was lengthwise three meters\\
		\glt `It was three meters long.'
	\end{xlist}
	
	\ex \label{lena3} \begin{xlist}
		\ex \gll Lena uvidela ne edinstvennogo krokodila, kotoryj byl v zooparke.\\
		Lena saw not only crocodile which was at zoo\\
		\glt `Lena saw one of the crocodiles at the zoo.'
		
		\ex \gll \# On byl dlinoy tri metra.\\
		{} it was lengthwise three meters\\
		\glt `It was three meters long.'
	\end{xlist}

	\ex \begin{xlist}
		\ex \gll Ol'ga poprobovala edinstvennyj tort, kotoryj byl na ve\v{c}erinke.\\
		Olga tasted only cake which was at party\\
		\glt `Olga tasted the only cake at the party.'

		\ex \gll On byl \v{s}okoladnyj.\\
		it was chocolate\\
		\glt `It was chocolate.'
	\end{xlist}

	\ex \begin{xlist}
		\ex \gll Ol'ga ne poprobovala edinstvennyj tort, kotoryj byl na ve\v{c}erinke.\\
		Olga not tasted only cake which was at party\\
		\glt `Olga didn't taste the only cake at the party.'
		
		\ex \gll On byl \v{s}okoladnyj.\\
		it was chocolate\\
		\glt `It was chocolate.'
	\end{xlist}
	
	\ex \label{olga3} \begin{xlist}
		\ex \gll Ol'ga poprobovala ne edinstvennyj tort, kotoryj byl na ve\v{c}erinke.\\
		Olga tasted not only cake which was at party\\
		\glt `Olga tasted one of the cakes at the party.'
		
		\ex \gll \# On byl \v{s}okoladnyj.\\
		{} it was chocolate\\
		\glt `It was chocolate.'
	\end{xlist}
\end{exe}

In summary, argumental anti-uniqueness effects arise in not only where they do in English---when DP-internal \textit{only} is in the scope of negation with a verb of creation---but with verbs of non-creation as well.

\subsection{No anti-uniqueness in some idiolects \label{sec:no-anti-unique}}
The data presented above will be analyzed in greater depth in section \ref{sec:existence-and-uniqueness}. But a set of limited but systematic counterexamples should be dealt with first. As noted previously, not all Russian speakers find the continuation in (\ref{anna3}) ungrammatical. The combination in (\ref{no-anti-unique}) is grammatical for these speakers, and similarly for (\ref{maria3}), (\ref{boris3}), (\ref{lena3}) and (\ref{olga3}).

\begin{exe}
	\ex \label{no-anti-unique} \begin{xlist}
		\ex \gll Anna posetila ne edinstvennuju lekciju, kotoruju pro\v{c}ital Xomskij, kogda byl v na\v{s}em universitete.\\
		Anna attended not only lecture which gave Chomsky when was at our university\\
		\glt `Anna went to one of the lectures Chomsky gave at our university.'
		
		\ex \gll Ona byla o lingvistike.\\
		it was about linguistics\\
		\glt `It was about linguistics.'
	\end{xlist}
\end{exe}

In order to express these sentences idiomatically in English, one has to resort to using the indefinite \textit{one of the lectures} in (\ref{no-anti-unique}), but in Russian the same definite descriptions is used as in (\ref{anna1}) and (\ref{anna2}).

How can it be that (\ref{no-anti-unique}) entails a multiplicity of lectures and yet allows for a singular reference? The first step towards answering this question is to clarify the syntactic structure of \textit{ne edinstvennyj lekciju} `not (the) only lecture.' The constituent negation particle \textit{ne} must either be outside the DP, as in (\ref{external-ne}), or internal to it, as in (\ref{internal-ne}).

\begin{exe}
	\ex \label{external-ne} Anna posetila ne [_{DP} edinstvennuju lekciju].
	\ex \label{internal-ne} Anna posetila [_{DP} ne edinstvennuju lekciju].
\end{exe}

The meaning of (\ref{no-anti-unique}) indicates that \textit{edinstvennyj} is being negated, since \textit{edinstvennyj} entails singularity while the matrix sentence entails multiplicity. It is not obvious how this semantic relationship could be explained if \textit{ne} were external to the DP, because a (phonetically null) determiner would intervene between \textit{ne} and \textit{edinstvennyj} and prevent them from composing directly. On the other hand, if both words were internal to the DP, then a compositional analysis would be natural.

In that case, it must be the DP \textit{ne edinstvennuju lekciju} (rather than \textit{edinstvennuju lekciju} with \textit{ne} outside) that refers to the lecture that Anna attended, out of the multiple lectures that were given.

This account raises a serious issue. \textit{Edinstvennuju lekciju} presumably denotes a singleton set. The negation particle \textit{ne} normally functions as the set complement operation, which means that \textit{ne edinstvennuju lekciju} ought to denote the complement of a singleton set, which would have more than one element. But a set with more than one element should not be able to be interpreted as determinate.

The difficulty is not so much a matter of an inexpressive theory as a true peculiarity in the facts of the Russian language in this instance. It is quite unusual that \textit{ne edinstvennuju lekciju} `the not-only lecture' can simultaneously entail a multiplicity of lectures while denoting a single one.

I suggest two approaches: one which makes use of a selection operation on sets to pick out a singular referent, and one which postulates an alternative set akin to those induced by adverbial \textit{only}.

What would be required in the semantics is some operation to pick out one of the multiplicity of goals. This selection operation, which would extract a singular referent from a multiplicity, must be constrained by the form of the rest of the sentence: \textit{ona} in (\ref{no-anti-unique}) may not refer to just any lecture that Chomsky gave, but specifically the one that Anna attended.

A phrase yielding an antecedent other than what it strictly denotes is not unknown in natural languages: complement anaphora are just such a phenomenon. A complement anaphor is a pronoun whose antecedent is the complement of some set previously denoted \citep{nouwen03, schwarz09}. In (\ref{kennedy}), the antecedent of \textit{they} in the second sentence is the complement of \textit{few congressmen}, i.e. few congressmen admire Kennedy so the majority of them think he is incompetent. Only certain quantifiers allow complement anaphora, as (\ref{kennedy2}) shows.

\begin{exe}
	\ex \label{kennedy} Few congressmen admire Kennedy. They think he's incompetent.
	\ex \label{kennedy2} A few congressmen admire Kennedy. \#They think he's incompetent.
\end{exe}

The same pattern holds in Russian:

\begin{exe}
	\ex \gll Malo kto iz kongressmenov vosxi\v{s}\v{c}aetsja Kennedi. Oni dumajut, \v{c}to on neumelyj.\\
	Few who from congressmen admire Kennedy they think that he incompetent\\
	\glt `Few congressmen admire Kennedy. They think he's incompetent.'
	\ex \gll Neskol'ko kongressmenov vosxi\v{s}\v{c}ajutsja Kennedi. \#Oni dumajut, \v{c}to on neumelyj.\\
	{A few} congressmen admire Kennedy they think that he incompetent\\
	\glt `A few congressmen admire Kennedy They think he's incompetent.'
\end{exe}

Complement anaphora illustrate that the antecedent of a pronoun need not always be explicitly present in the semantics, as long as it can be derived from some entity that is present. Complement anaphora involve the set complement relationship; the data from Russian suggests that some individual-selection operation on sets may also be available.

The second possibility is that \textit{edinstvennyj} induces an alternative set. Alternative sets were originally proposed to model the semantics of the DP-external use of \textit{only} \citep{rooth85, rooth92}.
A sentence with \textit{only} like (\ref{adverbial-only}) involves both the presupposition that Min-ji goes to the movies and the assertion that no one else does, where ``no one else'' is constrained to a set of plausible contextual alternatives to Min-ji.

\begin{exe}
	\ex \label{adverbial-only} Only Min-ji goes to the movies.
\end{exe}

Similarly, (\ref{no-anti-unique}) involves both a single lecture that Anna attended and a set of lectures which Anna did not attend. The phrase \textit{ne edinstvennyj lekciju} would behave similarly to the \textit{only Min-ji} in (\ref{adverbial-only}), in that both simultaneously entail multiplicity (multiple lectures, multiple people whose movie-going habits are under consideration) while denoting a single one (the lecture that Anna attended, Min-ji).

Under this account, \textit{ne edinstvennuju lekciju} would denote the single lecture that Anna attended, but would also carry an entailment about the alternative set, i.e. the additional lectures she did not attend.

The two approaches I have proposed are not incompatible. It could be that the set selection operation is sensitive to the alternative set that DP-internal \textit{only} induces in this case. At any rate, I hope to have made the ability of \textit{ne edinstvennuju lekciju} in some idiolects to entail multiple lectures but denote a single one a little less puzzling.