\documentclass{article}

\usepackage{verbatim}
\usepackage{natbib}
\bibliographystyle{linquiry2}
\usepackage{gb4e}

% Cite an author, e.g. Davidson's (1967)
\newcommand{\citegen}[1]{\citeauthor{#1}'s~(\citeyear{#1})}

\title{\textit{The only} and definiteness in English and Russian}
\author{Ian Fisher}
\date{}

\begin{document}
\maketitle

\noindent LING399 Presentation I at Haverford College, 5 October 2018.

\section{A puzzle}
Courtesy of \citet{cb2015}.

\begin{exe}
	\ex Scott is not the only author of \textit{Waverley}.
	\ex Anna didn't score the only goal.
\end{exe}

\section{Research questions}
\begin{itemize}
	\item What are the semantics of \textit{the only} constructions in English and in Russian?
	\item How do the semantics of \textit{the only} relate to definiteness?
	\item What is the relationship between regular \textit{only} and \textit{the only}?
\end{itemize}

\section{Russian data}
\subsection*{\textit{Tol'ko} and \textit{edinstvennyj}}
\begin{exe}
	\ex \gll \textbf{Tol'ko} studenty pri\v{s}li.\\
	\textbf{only} students came\\
	\glt `Only the students came.'
	\ex \gll Marija vzjala \textbf{edinstvennuju} knigu.\\
	Maria took \textbf{only} book.\\
	\glt `Maria took the only book.'
\end{exe}

\subsection*{Predicative anti-uniqueness}
\begin{exe}
	\ex \gll Tolstoj ne edinstvennyj avtor \textit{Vojny i mira}\\
	Tolstoy not only author \textit{War and Peace}\\
	\glt `Tolstoy is not the only author of \textit{War and Peace}.'
\end{exe}

\subsection*{Argumental anti-uniqueness}
\begin{exe}
	\ex Anna didn't score the only goal. *It was an excellent strike.
	\ex \gll Anna \textbf{ne} zabila edinstvennyj gol. On byl otlichnyj udar.\\
	Anna \textbf{not} scored only goal it was excellent strike\\
	\glt `Anna didn't score the only goal. It was an excellent strike.' (one goal)
	\ex \gll Anna zabila \textbf{ne} edinstvennyj gol. On byl otlichnyj udar.\\
	Anna scored \textbf{not} only goal it was excellent strike\\
	\glt `Anna didn't score the only goal. It was an excellent strike.' (multiple goals)
\end{exe}

\subsection*{Indefinite \textit{edinstvennyj}}
\begin{exe}
	\ex \gll U etoj kompanii --- (odin/??edinstvennyj) direktor\\
	At this company {} (one/only) director\\
	\glt `This company has a sole director.'
\end{exe}

\section{Analysis}
\begin{itemize}
	\item \textit{Only} and \textit{the only} are different words in Russian, suggesting that they may have different semantics.
	\item Anti-uniqueness effects are evident in predicative definites but not in argumental definites.
	\item Contrary to \citegen{cb2015} predictions, indeterminate readings for \textit{edinstvennyj} do not seem to be more widely available in Russian.
\end{itemize}

\begin{comment}
\subsection*{\citet{cb2015}}
\citegen{cb2015} proposal for the semantics of definites in English:

\begin{itemize}
	\item Definite descriptions are predicative (type $\langle e, t \rangle$).
	\item The indefinite and definite articles are identity functions. The definite article carries a weak uniqueness presupposition.
	\item Definite descriptions receive determinate meaning and argumental status through type-shifting \`{a} la \citet{partee86}.
\end{itemize}

\section{\textit{Only}, \textit{sole}, \textit{single} and \textit{one}}
Diagnostics adapted from \citet{cb2012a}.

\begin{exe}
	\ex \textbf{With indefinite article}: This company has a(n) (*only/sole/single/*one) director.
	\ex \textbf{With superlative}: Climate change is the (*only/?sole/single/??one) greatest threat to human life.
	\ex \textbf{With plural NP}: They are the (only/sole/*single/*one) people I trust.
	\ex \textbf{Licensing of NPIs}: The (only/?sole/??single/?one) truck I ever drove was red.
	\ex \textbf{DP negation}: Not a(n) (*only/sole/single/*one) person showed up.
\end{exe}

\noindent In summary:\\

\begin{tabular}{ c | c c c c c }
	& indefinite article & superlative & plural & licenses NPIs & DP negation \\
	\hline
	\textit{only} & no & no & yes & yes & no \\
	\textit{sole} & yes & yes & yes & yes & yes \\
	\textit{single} & yes & yes & no & marginal & yes \\
	\textit{one} & no & marginal & no & yes & no \\
\end{tabular}

Applying these diagnostics for Russian suggests that \textit{edinstvennyj}
\end{comment}

\section{Outlook}
\begin{itemize}
	\ex More data collection in Russian
	\ex Does \textit{edinstvennyj} correspond to \textit{only}, \textit{single}, \textit{sole}, or \textit{one}?
	\ex More research on negation and its interaction with \textit{the only}
\end{itemize}

\bibliography{thesis}

\end{document}