\documentclass{article}

\usepackage{natbib}
\bibliographystyle{linquiry2}
\usepackage{gb4e}

\title{DP-internal \textit{only} and definiteness in English and Russian}
\author{Ian Fisher}
\date{}

\begin{document}
\maketitle

\noindent LING399 Presentation II at Haverford College, 9 November 2018.

\section{My thesis}
An analysis of some interesting semantic and syntactic properties of DP-internal \textit{only} in English and in Russian. In particular:

\begin{itemize}
	\item Anti-uniqueness effects \citep{cb2015}
	\item Negative polarity item licensing
\end{itemize}


\section{Anti-uniqueness effects}
\begin{exe}
	\ex Scott is not the only author of \textit{Waverley}.
	\ex Anna didn't score the only goal.
\end{exe}

\noindent In Russian:
\begin{exe}
	\ex \gll Anna ne zabila edinstvennyj gol.\\
	Anna not scored only goal\\
	\glt `Anna didn't score the only goal.' (one goal)
	\ex \gll Anna zabila ne edinstvennyj gol.\\
	Anna scored not only goal\\
	\glt `Anna didn't score the only goal.' (multiple goals)
\end{exe}

\noindent Some speakers find these sentences ungrammatical.


\section{DP-internal \textit{only} and NPIs}
Downward-entailment (canonical environment for negative-polarity items):

\begin{exe}
	\ex $P(x)$ is a downward-entailing environment if $P(S)$ implies $P(S')$ for all subsets $S'$ of $S$.
\end{exe}

\noindent DP-internal \textit{only} licenses NPIs:

\begin{exe}
	\ex The only car he \textbf{ever} owned was a Subaru Legacy.
	\ex \gll Ivan vzjal edinstvennuju knigu, kotoruju \textbf{kto-libo} xotel.\\
	Ivan took only book which anybody wanted\\
	\glt `Ivan took the only book that anybody wanted.'
\end{exe}

\noindent Does DP-internal \textit{only} create a downward-entailing environment?

\begin{exe}
	\ex The only mountain greater than 29,000 feet tall is Everest.
	\ex The only mountain greater than 30,000 feet tall is Everest.
	\ex The only book in the library written by a Russian is already checked out.
	\ex The only book in the library written by Gogol is already checked out.
\end{exe}

\noindent Non-existence with other DE operators:

\begin{exe}
	\ex No reptiles give birth to live young.
	\ex No four-toed frilled iguanas give birth to live young.
\end{exe}

\noindent Generalization: Downward entailment for DP-internal \textit{only} holds, subject to the existence presupposition of the definite article.

\bibliography{thesis}

\end{document}