\documentclass{article}

\usepackage{verbatim}
\usepackage{natbib}
\bibliographystyle{linquiry2}
\usepackage{gb4e}

% Cite an author, e.g. Davidson's (1967)
\newcommand{\citegen}[1]{\citeauthor{#1}'s~(\citeyear{#1})}

\title{\textit{The only} and definiteness in English and Russian}
\author{Ian Fisher}
\date{}

\begin{document}
\maketitle

\noindent LING399 Presentation I at Haverford College, 5 October 2018.

\section{A puzzle}
Courtesy of \citet{cb2015}.

\begin{exe}
	\ex Scott is not the only author of \textit{Waverley}.
	\ex Anna didn't score the only goal.
\end{exe}

\section{Research questions}
\begin{itemize}
	\item What are the semantics of \textit{the only} constructions in English and in Russian?
	\item How do the semantics of \textit{the only} relate to definiteness?
	\item What is the relationship between regular \textit{only} and \textit{the only}?
\end{itemize}

\section{Russian data}
\subsection*{\textit{Tol'ko} and \textit{edinstvennyj}}
\begin{exe}
	\ex \gll \textbf{Tol'ko} studenty pri\v{s}li.\\
	\textbf{only} students came\\
	\glt `Only the students came.'
	\ex \gll Marija vzjala \textbf{edinstvennuju} knigu.\\
	Maria took \textbf{only} book.\\
	\glt `Maria took the only book.'
\end{exe}

\subsection*{Predicative anti-uniqueness}
\begin{exe}
	\ex \gll Tolstoj ne edinstvennyj avtor \textit{Vojny i mira}\\
	Tolstoy not only author \textit{War and Peace}\\
	\glt `Tolstoy is not the only author of \textit{War and Peace}.'
\end{exe}

\subsection*{Argumental anti-uniqueness}
\begin{exe}
	\ex Anna didn't score the only goal. *It was an excellent strike. (ambiguous)
	\ex \gll Anna \textbf{ne} zabila edinstvennyj gol. On byl otlichnyj udar.\\
	Anna \textbf{not} scored only goal it was excellent strike\\
	\glt `Anna didn't score the only goal. It was an excellent strike.' (one goal)
	\ex \gll Anna zabila \textbf{ne} edinstvennyj gol. On byl otlichnyj udar.\\
	Anna scored \textbf{not} only goal it was excellent strike\\
	\glt `Anna didn't score the only goal. It was an excellent strike.' (multiple goals)
\end{exe}

\subsection*{Indefinite \textit{edinstvennyj}}
\begin{exe}
	\ex \gll U etoj kompanii --- (odin/??edinstvennyj) direktor\\
	At this company {} (one/only) director\\
	\glt `This company has a sole director.'
\end{exe}

\section{Summary}
\begin{itemize}
	\item \textit{Only} and \textit{the only} are different words in Russian,  raising the possibility that they have different semantics.
	\item Anti-uniqueness effects are evident in predicative definites but not in argumental definites in Russian.
	\item Contrary to \citegen{cb2015} predictions, indeterminate readings for \textit{edinstvennyj} do not seem to be more widely available in Russian.
\end{itemize}

\section{Outlook}
\begin{itemize}
	\ex More data collection in Russian
	\ex Does \textit{edinstvennyj} correspond to \textit{only}, \textit{single}, \textit{sole}, or \textit{one}?
	\ex More research on negation and its interaction with \textit{the only}
\end{itemize}

\bibliography{thesis}

\end{document}