\documentclass{article}

\usepackage[a4paper]{geometry}

\usepackage{natbib}
\bibliographystyle{linquiry2}
\usepackage{gb4e}

\title{DP-internal \textit{only} in English and Russian}
\author{Ian Fisher}
\date{}

\begin{document}
\maketitle

\noindent LING399 Presentation II at Haverford College, 9 November 2018.

\section{Anti-uniqueness effects}
From \citet{cb2015}:

\begin{exe}
	\ex Anna didn't score the only goal.
\end{exe}

\noindent In Russian (note: some speakers find such sentences ungrammatical):
\begin{exe}
	\ex \gll Anna zabila ne edinstvennyj gol. On byl otlichnyj udar.\\
	Anna scored not only goal he was excellent strike\\
	\glt `Anna didn't score the only goal. It [her goal] was an excellent strike.'
\end{exe}

\noindent The puzzle: how can the sentence entail multiple goals, but refer to a single one?

\begin{exe}
	\ex $\exists x [ \textsc{Goal}(x) \land \textsc{Scored}(a, x) \land \forall y [ y \in \textsc{Alt}(x) \to \neg \textsc{Scored}(a, y)] ]$\\ where $a$ stands for \textit{Anna} and $\textsc{Alt}(x)$ for the set of alternatives to $x$.
\end{exe}


\section{DP-internal \textit{only} and NPIs}
DP-internal \textit{only} licenses negative polarity items:

\begin{exe}
	\ex The only car he \textbf{ever} owned was a Subaru Legacy.
	\ex \gll Ivan vzjal edinstvennuju knigu, kotoruju \textbf{kto-libo} xotel.\\
	Ivan took only book which anybody wanted\\
	\glt `Ivan took the only book that anybody wanted.'
\end{exe}

\noindent Does DP-internal \textit{only} create a downward-entailing environment? (California has about 39 million inhabitants.)

\begin{exe}
	\ex The only state with more than 30 million inhabitants is California.
	\ex The only state with more than 40 million inhabitants is California.
\end{exe}

\noindent Generalization: Downward entailment for DP-internal \textit{only} holds, subject to the existence presupposition of the definite article.

\bibliography{thesis}

\end{document}